---
title: "netflix_assignmnt"
author: "ozgur_akbelen"
date: "11/3/2021"
output: 
html_document:
df_print: paged
prettydoc::html_pretty:
theme: leonids
highlight: github
---

Installing packages which will need in further sections 
```{r}
install.packages("htmltab", repos = "http://cran.us.r-project.org")
install.packages("lubridate", repos = "http://cran.us.r-project.org")
install.packages("plotly", repos = "http://cran.us.r-project.org")
install.packages("dplyr", repos = "http://cran.us.r-project.org")
install.packages("tm", repos = "http://cran.us.r-project.org")
install.packages("prettydoc", repos = "http://cran.us.r-project.org")
```
Activating packages
```{r}
library("htmltab")
library("lubridate")
library("plotly")
library("dplyr")
library("tm")
library("prettydoc")
```

Reading data files from github to local pc
```{r}
urlfile<-'https://raw.githubusercontent.com/ygterl/EDA-Netflix-2020-in-R/master/netflix_titles.csv'
data<-read.csv(urlfile)
```
 
Create Explantion data table with plotly 
```{r}
explanation_table <- rbind(c('show_id', 'type', 'title', 'director', 'cast', 'country', 'date_added', 'release_year', 'rating' , 'duration', 'listed_in', 'description'), 
    c("Unique ID for movies", 
    "Movie or Tv Show ", 
    "Title of the Movie or TV Show", 
    "Director of the Movie /TV Show", 
    "List of Actors",
    "Where Movie or Tv show was produced",
    "Movie added date on Netflix",
    "Actual release year of Movie / TV Show",
    "Rating of Movie or TV Show",
    "Total Duration - in minutes or number of seasons",
    "Genre",
    "The summary"))

description_table <- plot_ly(
  type = 'table',
  columnorder = c(1,2),
  columnwidth = c(12,12),
  header = list(
    values = c('<b>VARIABLES</b><br>', '<b>DESCRIPTION</b>'),
    line = list(color = '#000000'),
    fill = list(color = '#fff2cc'),
    align = c('left','center'),
    font = list(color = 'black', size = 15),
    height = 40
  ),
  cells = list(
    values = explanation_table,
    line = list(color = '#506784'),
    fill = list(color = c('#C9DFEC', 'white')),
    align = c('left', 'left'),
    font = list(color = c('#000000'), size = 15),
    height = 30
    ))
description_table

```
Cleaning dataframe
Deleting unnecessary variable "show_id"
Changing date format
Removing Na's and duplicate datas from database
Changing variable formats as factor
```{r}
data <- data [-1]
data$date_added <- mdy(data$date_added)
data <- distinct(data ,director, title, country, type, release_year, .keep_all = TRUE)
data$type <- as.factor(data$type)
```

Total number of TV series and movies by year.
```{r}
data_release <- data %>% group_by(release_year) %>% summarise(
  count = n())
summary(data_release)

```

Visualization of Total number of TV series and movies by year with GGplot 2 library; Y axis changed by log 10 base.
```{r}
ggplot(data_release, aes(x=release_year, y=count)) + 
  ylim(0,max(data_release$count)) +
  ggtitle("Number of Movie and TV Show in time scale") +
  xlab("Year") + 
  ylab("Log10 Number of Movie and TV Show")+
  scale_x_continuous(limits = c(1925, 2020, 25)) +
  scale_y_log10()+
  geom_point(aes(color=count))
  
```
Which TV show and movie genres are the most in Netflix?
```{r}
data_genre <- strsplit(data$listed_in, split = ", ")
data_genre <- data.frame(type = rep(data$type, sapply(data_genre, length)), genre = unlist(data_genre))
data_genre$genre <- as.character(data_genre$genre)

sum_of_genre <- na.omit(data_genre) %>%
  group_by(genre, type) %>%
  summarise(count = n())

plot_ly(sum_of_genre, x= ~genre, y= ~sum_of_genre$count, type = "bar" )%>%
  layout(title = 'Genres on Netflix',font= 24, plot_bgcolor = "#e5ecf6", xaxis = list(title = 'Genres'), yaxis = list(title = 'Sum of Genres'))
```